---
title: "UNGA 03a - Creation of a Sample Corpus"
author: "Christoph Leonhardt"
date: "12 March 2019"
output: html_document
---

## Prep

```{r setup}
library(polmineR)
use("UNGA")
corpus_new <- "UNGAMINI"

s_attrs <- s_attributes("UNGA")

p_attrs <- p_attributes("UNGA")

registry <- Sys.getenv("CORPUS_REGISTRY")
if (!file.exists(registry)) stop("environment variable CORPUS_REGISTRY needs to be defined")
stateparl_registry_file <- file.path(registry, tolower(corpus_new))
if (file.exists(stateparl_registry_file)) file.remove(stateparl_registry_file)

data_dir <- file.path(dirname(registry), "indexed_corpora")
if (!file.exists(data_dir)) dir.create(data_dir)
stateparl_data_dir <- file.path(data_dir, tolower(corpus_new))
if (!file.exists(stateparl_data_dir)) dir.create(stateparl_data_dir)
file.remove(list.files(stateparl_data_dir, full.names = TRUE))

```



## Sampling

Using the entire UNGA corpus (see 1_2019_01_23_UNGA_tei_to_cwb.Rmd), we create a sample corpus (UNGAMINI) to demonstrate some features.

```{r}
library(data.table)
library(cwbtools)
```

Let's assume that 0.5% of UNGA's volume would be appropriate both as an illustrative sample and in terms of file size in an R package which shouldn't exceed 5mb. We want to draw a random sample from the days UNGA covers.

```{r}
size("UNGA") # UNGA comprises 40 million tokens

no_of_days_to_sample <- round(length(s_attributes("UNGA", "date"))/200)
set.seed(111)
random_days <- sample(s_attributes("UNGA", "date"), size = no_of_days_to_sample)
```

Next, we want to build a partition which contains the random days from above.

```{r}
date_regex <- paste0(random_days, collapse = "|")
sample_partition <- partition("UNGA", date = date_regex, regex = TRUE) 
size(sample_partition) # 330000 tokens
size(sample_partition)/size("UNGA")*100
```

## Decoding

```{r}

s_attribute_dt <- polmineR::decode(sample_partition)
s_attribute_dt[, cpos :=  as.character(as.integer(factor(cpos)) - 1)][, struc :=  as.character(as.integer(factor(struc)) - 1)]
tokenstream_dt <- copy(s_attribute_dt)
tokenstream_dt <- tokenstream_dt[, c("word", "pos", "lemma", "ner", "id", "cpos")]

s_attribute_dt[, c("word", "lemma", "pos", "ner") := NULL]
s_attribute_dt <- s_attribute_dt[,{list(cpos_left = min(as.integer(.SD[["cpos"]])), cpos_right = max(as.integer(.SD[["cpos"]])), 
                                    id = unique(.SD[["id"]]),
                                    speaker = unique(.SD[["speaker"]]),
                                    state_organization = unique(.SD[["state_organization"]]),
                                    role = unique(.SD[["role"]]),
                                    unga_session = unique(.SD[["unga_session"]]),
                                    unga_meeting = unique(.SD[["unga_meeting"]]),
                                    date = unique(.SD[["date"]]),
                                    year = unique(.SD[["year"]])
                                    )}, by = "struc"]

```

## Corpus Encode

```{r}
CD <- CorpusData$new()
CD$tokenstream <- tokenstream_dt
CD$metadata <- s_attribute_dt
CD$metadata$lp <- as.character(CD$metadata$lp)
CD$metadata$session <- as.character(CD$metadata$session)
CD$metadata$year <- as.character(CD$metadata$year)

message("... start encoding")

CD$encode(
  registry_dir = registry, data_dir = stateparl_data_dir,
  corpus = toupper(corpus_new), encoding = "utf8", method = "R",
  p_attributes = p_attrs, s_attributes = s_attrs,
  compress = TRUE
)

message("... save tar.gz")

cwbtools::corpus_as_tarball(corpus=corpus_new, registry_dir = Sys.getenv('CORPUS_REGISTRY'), tarfile='~/lab/tmp/ungamini.tar.gz')

```