--- 
output: github_document
bibliography: ./vignettes/literature.bib
---

[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Travis-CI Build Status](https://api.travis-ci.org/PolMine/unga.svg?branch=master)](https://travis-ci.org/PolMine/unga)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/PolMine/unga?branch=master&svg=true)](https://ci.appveyor.com/project/PolMine/unga)


# UN General Assembly Corpus

## About 

The United Nations offer pdf documents of the verbatim records of the [United Nations General Assembly (UNGA)](https://www.un.org/en/ga/). Based on a machine-readable XML version of the documents prepared in the PolMine Project, a linguistically annotated version of the corpus has been imported into the Corpus Worbench (CWB). The R Data Package 'UNGA' offers a convenient mechanism to download the full UNGA corpus. It has been developed primarily to be used in combination with the polmineR package which offers a basic vocabulary to work with large linguistically annotated corpora.

Note that the R package includes only a small sample corpus. The primary functionality of the package is to download the full corpus from an online storage place (amazon S3). The data will be stored within the directory structure of the package.


## Installation

The easiest way to install the *UNGA* package is to install it from the
[drat](https://CRAN.R-project.org/package=drat)-repository
of the [PolMine Project](http://www.polmine.de).

```{r, eval = FALSE}
install.packages("UNGA", repos = "https://polmine.github.io/drat")
```

The package  includes only a installer function `unga_download_corpus()`
that will download the UNGA corpus from the instance where it is stored (amazon S3).

```{r download_corpus, eval = FALSE}
UNGA::unga_download_corpus()
```

Note that the size of the tarball with the corpus that is amounts to about 500 MB. Take care that your internet is sufficiently robust and fast. The indexed corpus will be stored in a subdirectory of the package (./extdata/cwb/).


## Usage

The idea to use R packages for shipping corpora has been developed in the context
of the PolMine Project [@blaette2018]. The most convenient way to use the data
will be to use the [polmineR](https://CRAN.R-project.org/package=polmineR) package.
To be able to access that data within the package, call the `use()`-function.

```{r, eval = FALSE}
if (!"polmineR" %in% rownames(installed.packages())) install.packages("polmineR")
library(polmineR)
use("UNGA")
```

If the corpora have been downloaded, you should see something like this.

```{r use_unga, echo = FALSE}
library(polmineR)
use("UNGA")
```

The polmineR package offers a basic vocabulary for corpus analysis (counting,
keyword-in-context analysis, cooccurrences, keyword extraction etc.). To learn
more about the polmineR package, consult the [package documentation](http://polmine.github.io/polmineR/).

Just to check that polmineR works, you might want to perform a simple counting 
operation, such as counting the number of occurrences of "sustainable development"
using the syntax of the Corpus Query Processor (CQP).

```{r}
count("UNGA", query = '"sustainable" "development" %c', cqp = TRUE)
```


## Disclaimer

The UNGA corpus has been prepared to serve as test data for the polmineR package: A
corpus of the UN General Assembly is most international test resource that occurred 
to us. The language resource has not yet gone through extensive quality checks!
Data quality should be sufficient for text mining exercises, but further improvements
may be necessary to develop  the corpus into a trustworthy research resource for 
research on international relations (IR) and international organizations.

If you have feedback on the data, please use the issue tracker of this repository!

It is our understanding that in line with the Freedom of Information, a principle firmly
established in the UN system, the verbatim records of the UN General Assembly are in
the public domain. Please note, however, that the legal status of the UNGA corpus is not
yet defined.


## References


